---
title: "Vignette of the a4Core package"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float:
      collapsed: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{a4Core package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Introduction

This document explains the functionalities available in the
**a4Core** package.


This package contains utility functions for the Automated Affymetrix Array Analysis 
suite of packages.

```{r options, echo = FALSE}
	
	library(knitr)
	opts_chunk$set(echo = TRUE, results = 'asis', warning = FALSE, 
		error = FALSE, message = FALSE, cache = FALSE,
		fig.width = 8, fig.height = 7,
		#out.width = '0.7\\textwidth', 
		fig.align = 'center')#, out.height = 0.5\\textwidth', fig.path = 'graphs/') 
	options(width = 170)#, stringsAsFactors = FALSE
	options(warn = 1)#instead of warn = 0 by default -> to have place where warnings occur in the call to Sweave function
	
```

```{r loadLibraries, results = 'hide', echo = FALSE}

	library(a4Core)

```

# Simulate data

An expressionSet example data for testing and demonstration of the set of packages is simulated with
the `simulateData` function:

```{r simulateData}
eSet <- simulateData(
	nCols = 40, nRows = 1000, 
	nEffectRows = 5, nNoEffectCols = 5,
	betweenClassDifference = 1, withinClassSd = 0.5
)
print(eSet)
```

# Top tables utility functions for classification

The package contains utility functions to create the top tables
of the most important features for multiple classification models
as produced by the `lassoClass` function of the `a4Classif` package, 
as 'glmnet', 'lognet' and 'elnet'.

# Appendix

## Session information

````{r sessionInformation, echo = FALSE}
print(sessionInfo())
```